CMSAC_reveal_js

### 2025-10-17 CMSAC_presentation/CMSAC_reveal_js.qmd
Updated with fragments.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tinytex)
library(tidyverse)
load("curves_data.RData")
#load("tournament_comparison_plot.png")
#load("tournament_comparison_plot_close.png")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tinytex)
library(tidyverse)
library(combinat)
load("curves_data.RData")
#load("tournament_comparison_plot.png")
#load("tournament_comparison_plot_close.png")
```

##

::::: columns
::: {.column width="50%"}
```{r}
knitr::include_graphics("4 bracket good.png")
```
:::

::: {.column width="50%"}
::: {.fragment}
```{r}
knitr::include_graphics("Mens-Basketball-Olympics-Getty-H-2024.jpeg")
```

:::

::: {.fragment}

```{r}
knitr::include_graphics("five_rec_league_men_playing_basketball.png")
```

:::

::: {.fragment}

```{r}
knitr::include_graphics("jv_girls_basketball.png")
```

:::

::: {.fragment}

```{r}
knitr::include_graphics("five_babies_playing_basketball.png")

```
:::

:::
:::::

##

::::: columns
::: {.column width="50%"}
Good
:::

::: {.column width="50%"}
Bad
:::
:::::

```{r}
knitr::include_graphics("4 seeded tourn w arrow.png")
```
